---
title: "AY_ClassProject_FramingAI"
author: "AY Kuwornu"
date: "2024-11-12"
output: html_document
---

AI & Disaster Framing through Organizational Press Releases

#Loading relevant packages and libraries
```{r}
# Install the striprtf package (if not installed)
install.packages("striprtf")
# Install the readtext package (if not installed)
install.packages("readtext")
# Load the library
library(readtext)
# Load the library
library(striprtf)

```

##Loading articles for study

```{r}
# Read and extract plain text from the .rtf file
file_path <- "C:/Users/elikp/OneDrive/Desktop/My_R_Class/AYClassProjectRepo/FramingAI_data/data_one/framingAI (1).RTF"
#writeLines writes this text to a text file
writeLines(text, "C:/Users/elikp/OneDrive/Desktop/My_R_Class/AYClassProjectRepo/FramingAI_data/data_one/framingAI (1).txt")

text_data <- readLines(file_path)%>% strip_rtf()
# View the plain text content
print(text_data)
```

##

You can also embed plots, for example:

```{r}


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
# Install the striprtf package (if not installed)
install.packages("striprtf")

# Load the library
library(striprtf)

